Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/discussion.tex
add some discussion

Throughout all the attempts of replication and validation, we face multiple challenges that started with the complexity of the system of study. In both papers we have systems that we were not able to fully 
model using \pygbe. For the case of Rockstuhl et al.\ the numerical method was the same, but the it was a 2D model instead of 3D like the one of \pygbe, while the computational work presented in Ellis et al.\ used a volumetric 
method, instead of a surface one like in \pygbe. Both works computed (or measured) quantities that were not the extinction cross section, but since there is a relation between their variables (scattering cross section or reflection)  
and ours (extinction cross section), through the wavelength (or wavenumber) at which the peaks happen, we have the quantity of interest in common. However, to produce the end results to compare against these works, we went through an 
exhaustive process of modeling, since we did not count with any information regarding the solvers, discretization, mesh, etc. In the case of Ellis et al. \ we benefited from multiple communications with some of the authors, 
who made available the geometry and mesh of the pillar, as well as the dielectric data needed as input for the simulations. Even though we appreciate this gesture, replication studies should not rely on communications with the authors. 
In both cases the secondary data that they use to achieve the results were not publicly available and we relied on a digitized version of them that we obtained. This work is tedious and introduce a lot of uncertainties that would be avoided by releasing 
the secondary data too.

Validation has been a hard thing to achieve for our solver since the field does not count with benchmarks that are meant to be used for validation. Multiple times
we encounter experimental results that we aim to replicate, but due to the lack of report on the conditions of the experiment, its setup and the geometries involved, 
we have not been able to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors made possible to 
attempt the validation.

(try to connect all this challenges with what we wrote in the background about replication, we touch on all those bullet points)

>>>>

Throughout all the attempts of replication and validation, we face multiple challenges that started with the complexity of the system of study. In both papers we have systems that we were not able to fully 
model using \pygbe. For the case of Rockstuhl et al.\ even though they used boundary element methods it was a 2D model instead of 3D like the one implemented in \pygbe. The computational work presented in Ellis et al.\ used a volumetric 
method, while \pygbe is a surface one. Both works computed (or measured) quantities that were not the extinction cross section (computed in \pygbe), but since there is a relationship between their variables (scattering cross section and reflection)  
and ours (extinction cross section), via the wavelength (wavenumber) at which resonance happens, this was not a problem. However, to produce the end results to compare against these works, we went through an 
exhaustive process of modeling, assumptions making and even corrections. We did not count with any information regarding the solvers, discretization, meshes, etc. In the case of Ellis et al. \ we benefited from multiple communications with the authors, 
who made available the geometry and mesh of the pillar, as well as the dielectric data used as input for the simulations. Even though we appreciate this gesture, replication studies should not rely on communications with the authors. 
In both cases the secondary data that presented in their results were not publicly available and we relied on a digitized version of them that we obtained. This work is tedious and introduce a lot of uncertainties that would be avoided by releasing 
the secondary data too.

Validation has been a hard thing to achieve for our solver since the field does not count with benchmarks that are meant to be used for validation. Multiple times
we encounter experimental results that we aim to replicate, but due to the lack of report on the conditions of the experiment, its setup and the geometries involved, 
we have not been able to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al. \ made 
possible the validation.
